
\documentclass[10.1pt,a4paper,sans]{moderncv}     
\moderncvstyle{banking}                         
\moderncvcolor{blue}            
\usepackage[utf8]{inputenc} 
\usepackage[scale=0.75, top=.6in, bottom=.3in, right=.7in, left=.7in]{geometry}

\usepackage{import}
\renewcommand*{\httplink}[2][]{
  \ifthenelse{\equal{#1}{}}
    {\href{#2}{#2}}
    {\href{#2}{#1}}}
\name{Simranpreet}{Singh}
\address{\centerline{
\#235, Street \#5, Bachittar Singh Nagar, Near Gne College, Gill Road, Ludhiana - 141006, Punjab, India
}}
\phone[mobile]{+91 842 788 9918}        
\email{simranlotey01@gmail.com}
\social [github][https://github.com/simranlotey]{https://github.com/simranlotey}
\homepage {https://simranlotey.github.io}
\homepage{https://linkedin.com/in/simranlotey}        
\begin{document}
\makecvtitle
\vspace{-30pt}
\section{Executive Summary}

\vspace{3pt}

\textit{\large{I enjoy both design and development. Being an computer application with skill in both these domains, I keep the balance between form and function and pay special attention to technical aspects as well as UI/UX and typography of every project.}}


\section{Education}

\vspace{3pt}

\begin{itemize}

\item{\cventry{2019--2022}{Guru Nanak Institute Of Management And Technology}{Bachelors's in Computer Application}{}{\textit{Punjab, India}}{}}

\item{\cventry{2017--2019}{Dasmesh Senior Secondary School}{Higher Secondary Examination (Non-Medical)}{}{\textit{Punjab, India}}{}}  % arguments 3 to 6 can be left empty

\item{\cventry{2016--2017}{Dasmesh Senior Secondary School}{Matriculation}{}{\textit{Punjab, India}}{}}

\end{itemize}

\section{Projects}

\vspace{3pt}

\begin{itemize}

\item{\cventry{2021}{\href{https://github.com/simranlotey/react-news-app.git}{\textcolor{blue}{https://github.com/simranlotey/react-news-app.git}}}{News App}{ReactJS based project}{}{\vspace{3pt}I have created a daily news app. In this i have used API \href{https://newsapi.org}{\textcolor{blue}{(https://newsapi.org)}}}}

\vspace{3pt}

\item{\cventry{2021}{\href{https://github.com/simranlotey/react-currency-converter.git}{\textcolor{blue}{https://github.com/simranlotey/react-currency-converter.git}}}{Currency Converter App}{ReactJS based project}{}{\vspace{3pt}I have created a currency converter app using API  \href{https://currencyconverterapi.com}{\textcolor{blue}{(https://currencyconverterapi.com)}}}}

\vspace{3pt}

\item{\cventry{2020}{\href{https://github.com/simranlotey/simranlotey.github.io.git}{\textcolor{blue}{https://github.com/simranlotey/simranlotey.github.io.git}}}{Portfolio}{HTML, CSS, JS based project}{}{\vspace{3pt}My Portfolio  \href{https://simranlotey.github.io}{\textcolor{blue}{(https://simranlotey.github.io)}}}}

\vspace{3pt}

\item{\cventry{2020}{\href{https://github.com/simranlotey/Blood-Bank-Management-System.git}{\textcolor{blue}{https://github.com/simranlotey/Blood-Bank-Management-System.git}}}{Blood Bank Management System}{Django based project}{}{}}

\end{itemize}


\section{Skillset}

\vspace{3pt}
 
\begin{itemize}

\item \textbf{Technologies I worked in:} HTML5, CSS, Bootstrap, Tailwind CSS, SCSS, SASS, MaterializeCSS, styled-components, JavaScript, Material UI, ReactJS, Redux, UI/UX, LaTeX.
\item \textbf{OS:} Linux, MS Windows.
\item \textbf{Language:} English, Punjabi, Hindi.
\item \textbf{Tools:} Visual Studio Code, Sublime, nano editor, vim editor, git.
\end{itemize}


\section{Achievements}

\vspace{3pt}

\begin{itemize}

\item \textbf{Wartech Competition,} I took part in wartech competition from GNIMT college and i got the first position in web development. I created a mobile shopee website in the competition.
\item \textbf{Head of web development in college,} I teach HTML, CSS, Bootstrap, JavaScript, ReactJS to the students.
\item \textbf{Head of IT Club in college.}
\item \textbf{freeCodeCamp,} I have completed responsive web design course.
\item \textbf{Certificate,} I have many certificate for web developement courses.
\item \textbf{Hacktoberfest,} Hacktoberfest participate.

\end{itemize}


\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        
\end{document}
